Modeling

### 2020-10-14 police_modeling.Rmd
First commit

---
title: "Police EDA"
author: Connie Wu
output: html_document
---

@@

```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
```

## Load Data
```{r load-data}
all <- read.csv("allshootingsdata.csv")

@@

## Exploratory Data Analysis

@@

```{r fatal-eda}
temp <- all %>% 
  group_by(Fatal) %>% 
  summarise(count = n())

ggplot(temp, aes(x=Fatal, y=count)) + 
  geom_bar(stat="identity") + 
  labs(x = "Fatal", y = "Count", title = "Counts for Fatal vs. Non-Fatal Police Shootings") 
```

```{r race-eda}
temp <- all %>% 
  group_by(Fatal, SubjectRace) %>% 
  summarise(race_count = n())

ggplot(temp, aes(x=SubjectRace, y=race_count, fill = Fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Race", y = "Count", title = "Counts for Victim Race by Fatal vs. Non-Fatal in Police Shootings")

temp2 <- all %>% 
  group_by(Fatal, OfficerRace) %>% 
  summarise(race_count = n())

ggplot(temp2, aes(x=OfficerRace, y=race_count, fill = Fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Race", y = "Count", title = "Counts for Officer Race by Fatal vs. Non-Fatal in Police Shootings") 
```

```{r gender-eda}
temp <- all %>% 
  group_by(Fatal, SubjectGender) %>% 
  summarise(gender_count = n())

ggplot(temp, aes(x=SubjectGender, y=gender_count, fill = Fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Gender", y = "Count", title = "Counts for Victim Gender by Fatal vs. Non-Fatal in Police Shootings")

temp2 <- all %>% 
  group_by(Fatal, OfficerGender) %>% 
  summarise(gender_count = n())

ggplot(temp2, aes(x=OfficerGender, y=gender_count, fill = Fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Gender", y = "Count", title = "Counts for Officer Race by Fatal vs. Non-Fatal in Police Shootings") 
```

```{r weapon-eda}
temp <- all %>% 
  group_by(Fatal, weapon) %>% 
  summarise(count = n())

ggplot(temp, aes(x=weapon, y=count, fill = Fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Weapon Type", y = "Count", title = "Counts of Each Weapon Type on Victims by Fatal vs. Non-Fatal in Police Shootings") 
```

```{r clean-cities}
cinn <- cincinnati %>% 
  select(RACE, SEX, TYPE) %>% 
  rename(race = RACE, gender = SEX, fatal = TYPE) %>% 
  mutate(city = "Cincinnati")

phil <- philly %>% 
  select(race, sex, fatal) %>% 
  rename(gender = sex) %>% 
  mutate(city = "Philadelphia")

comp <- rbind(cinn, phil)

comp <- comp %>%
  filter(race != "UNKNOWN") %>% 
  filter (race != "") %>% 
  filter(race != "UNK") %>% 
  filter(gender != "")

comp$race[comp$race == "WHITE"] <- "W"
comp$race[comp$race == "BLACK"] <- "B"
comp$race[comp$race == "OTHER"] <- "O"
comp$race[comp$race == "HISPANIC"] <- "H"

comp$gender[comp$gender == "MALE"] <- "M"
comp$gender[comp$gender == "FEMALE"] <- "F"

comp$fatal[comp$fatal == "0"] <- "N"
comp$fatal[comp$fatal == "1"] <- "F"
comp$fatal[comp$fatal == "NONFATAL"] <- "N"
comp$fatal[comp$fatal == "FATAL"] <- "F"
```

```{r fatal-eda}
temp <- comp %>% 
  group_by(fatal) %>% 
  summarise(count = n())

ggplot(temp, aes(x=fatal, y=count)) + 
  geom_bar(stat="identity") + 
  labs(x = "Fatal", y = "Count", title = "Counts for Fatal vs. Non-Fatal Police Shootings") 
```
```{r race-eda-cities}
temp <- comp %>% 
  group_by(fatal, race) %>% 
  summarise(count = n())

ggplot(temp, aes(x=race, y=count, fill = fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Race", y = "Count", title = "Counts for Victim Race by Fatal vs. Non-Fatal in All Shootings") 
```

```{r gender-eda-cities}
temp <- comp %>% 
  group_by(fatal, gender) %>% 
  summarise(count = n())

ggplot(temp, aes(x=gender, y=count, fill = fatal)) + 
  geom_bar(position="dodge", stat="identity") + 
  labs(x = "Gender", y = "Count", title = "Counts for Victim Gender by Fatal vs. Non-Fatal in All Shootings") 
```

>>>>

---
title: "Modeling"
author: "Connie Wu"
date: "10/13/2020"
output: html_document
---

@@

## Modeling
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
```

```{r load-data}
all <- read.csv("allshootingsdata.csv")

@@

@@
